---
title: "E-Cigs Webscrape"
author: "Bryan Adams"
date: "November 7, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(RSelenium)
library(jsonlite)
library(purrr)
```

# Webscrape an image from google image search

This is a working script that will save the first one hundred images.  I still need to work out saving the file name (that is predicting the weird names images will be since files do not like to have different symbols in them)

## Setting up the driver

```{r}
driver = rsDriver(browser = 'firefox')
remote_driver = driver$client
```

## Inputting the search term

```{r}
search_term = "e-cig"
```

## Navigating to the first image page

```{r}
url = paste0("https://www.google.com/search?q=", search_term,"&source=lnms&tbm=isch")
remote_driver$navigate(url)
```

## This gets the first 100 images.  I will adjust it to grab more images.

```{r}
images = remote_driver$findElements(using = "class name", value = "rg_meta")
```

```{r}


image_downloader = function(image){

  json_info = fromJSON(image$getElementAttribute('innerHTML')[[1]])
  
  image_url = json_info$ou
  
  name = json_info$pt
  
  download.file(image_url, paste0(name,".jpg"), mode = "wb")

}

images%>%
  map(image_downloader)


```